---
title: "Developing Data Products: Week 4 Assignment"
author: "Abhishek Dubey"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Project Summary
I have built a simple reactive application, which loads the data on action of dropdown selection of predefined datasets. It is a single page application, which has following components-

1. Sidebar Panel- Sidebar panel has 2 input controls-
    + Input Text box for page title selection.
    + Dropdown for dataset selection.

2. Main Panel: Main Panel has 2 tabs-
    + Data Snapshot- This tab shows the data in data table format. The R package DT provides an R interface to the JavaScript library DataTables. R data objects (matrices or data frames) can be displayed as tables on HTML pages, and DataTables provides filtering, pagination, sorting, and many other features in the tables. 

    + Data Summary- This tab shows inter quartile range of the data.

## Reactivity
The reactive expression depends on the input expression input:dataset, and that it's used by two output expressions- output:summary and output$view. Try changing the dataset (using Choose a dataset) while looking at the reactive and then at the outputs; you will see first the reactive and then its dependencies flash.

Notice also that the reactive expression doesn't just update whenever anything changes--only the inputs it depends on will trigger an update. Change the "Caption" field and notice how only the output$caption expression is re-evaluated.


## Slide with R Output
This page shows summary of BostonHousing data 

```{r cars, echo = TRUE}
library(mlbench)
library(DT)
data("BostonHousing")
view <- DT::renderDataTable({BostonHousing})
DT::dataTableOutput("view")
summary(BostonHousing)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

